**Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability**

### 2025-06-05 paper/5_Collabra/manuscript.qmd
Update manuscript.qmd

The original or refined version of the PHQ-4 was followed by the BDI-II, STAI-5, IAS, and MAIA-2, presented in random order. The IAS and the MAIA-2 were included as part of another study focused on interoception, and were only used in this stud as part of data quality control checks.

>>>>

The original or refined version of the PHQ-4 was followed by the BDI-II, STAI-5, IAS, and MAIA-2, presented in random order. The IAS **(ref?)** and the MAIA-2 **(ref?)** were included as part of another focused on interoception, and were only used in this study as part of data quality control checks.
